Dynamics of thin liquid film flows studied with a lattice Boltzmann method

### 2021-06-30 others/abstract.tex
Hmm

\begin{abstract}
\textbf{Abstract}
Thin liquid film flows are encountered in our every days life in many occasions.
Starting from large weather systems on planetary scales reaching down to wetting problems on the nano scale. 
This so called scale invariance is what makes the thin film equation or in other words, the lubrication approximation a valuable tool to study flows.

@@

\end{abstract}

>>>>

\begin{abstract}
\section*{Abstract}
Thin liquid film flows are encountered in our every days life in many occasions.
Starting from large weather systems on planetary scales ($10^6$m) reaching down to wetting problems on the nanometric scale ($10^{-9}$m). 
That a single set of equations can describe both the movement of atmospheric layers as well as the displacment of the contact line of a droplet with a diameter smaller than a micron ($10^{-6}$m)  is highly non trivial and related to the scale invariant nature of flow problems.

@@

\section*{Kurzfassung}
Thin liquid film flows are encountered in our every days life in many occasions.
Starting from large weather systems on planetary scales reaching down to wetting problems on the nano scale. 
This so called scale invariance is what makes the thin film equation or in other words, the lubrication approximation a valuable tool to study flows.

Over the past two decades numerical techniques have been developed to study this kind of systems.
Within this work a novel approach based on the lattice Boltzmann method (LBM) will be introduced.
This numerical tool is tested against known thin film results, such as instabilities, substrate dewetting and droplet flows.
Further new insights on the stochastic thin film equation will be shown and discussed.
\end{abstract}
